PM Mungbean meta-analysis

### 2021-01-18 02_Preliminary_analysis.Rmd
remove commented lines and add flextable library to load

```{r PA_Libraries, include=FALSE, message=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               bomrang,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra,
               here)

@@

```{r Full_Trial_Summary_table}
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%

   # filter(location == "Bongeen_1")%>%
   # select(PM_sev_treat,
   #        trial_ref,
   #          location,
   #          year,
   #          planting_date,
   #          first_sign_disease)

   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
             max_PM_yeild = max(PM_y_treat, na.rm = TRUE)
             )%>%
   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf

>>>>

```{r PA_Libraries, include=FALSE, message=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               bomrang,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra,
               flextable,
               here)

@@

```{r Full_Trial_Summary_table}
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
             max_PM_yeild = max(PM_y_treat, na.rm = TRUE),
             )%>%
   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
